Verification of a TCP/IP stack

### 2021-05-18 SecDev21/paper.tex
more fixes

In this paper, we take a practical approach, where the security of an existing TCP/IP stack implementation written in ANSI C programming language is incrementally enhanced by replacing parts of its code with formally verified code in SPARK \cite{mccormick_chapin_2015}. SPARK 2014 is a programming language designed as a subset of the Ada language to produce highly reliable software through formal verification. 
For this work, the CycloneTCP, a professional-grade embedded TCP/IP library developed by the Oryx Embedded company\footnote{\url{https://www.oryx-embedded.com/products/CycloneTCP.html}}. \Cref{Fig:TcpStack} shows the protocols implemented in the library. In this work, we focused on enhancing the TCP and socket components of the stack. The TCP implementation is meant to conform with the RFC 793 protocol specifications \cite{rfc793}. The quality of the C implementation hailed in the AMNESIA:33 report \cite{AMNESIA33} as one of the most resilient TCP/IP stack. Using a starting point, an existing well-tested and widely used TCP/IP implementation, the IoT industry can have an immediate benefit by adopting the proposed by this work security-enhanced version of this implementation.

@@

Initially described by the ``fathers of the Internet'' Vincent Cerf and Bob
Kahn, the TCP protocol was standardized in 1981 in~\cite{rfc793}.
Its sturdiness still makes it one of the most widely used protocols 40 years
later. Indeed, almost any networking application is using either the TCP or the
UDP protocols to traffic data between the Network and the Application layers.

@@

\subsection{TCP state machine}

Generally, every TCP communication session will go through the following three
phases (if no error occurs): 1)~opening the connection 2)~sending and receiving
the data and 3)~closing the connection.

The behavior of the three-phase communication can be described by the state
machine in figure~\ref{Fig:statemachine}.

>>>>

In this paper, we take a practical approach, where the security of an existing TCP/IP stack implementation written in ANSI C programming language is incrementally enhanced by replacing parts of its code with formally verified code in SPARK \cite{mccormick_chapin_2015}. SPARK 2014 is a programming language designed as a subset of the Ada language to produce highly reliable software through formal verification. For this work, the CycloneTCP, a professional-grade embedded TCP/IP library developed by the Oryx Embedded company \cite{CycloneTCP}. \Cref{Fig:TcpStack} shows the protocols supported by the library. This work focuses on the TCP and socket components of the stack. The library's TCP implementation is meant to conform with the RFC 793 protocol specifications \cite{rfc793}. The quality of the CycloneTCP is acknowledged by the AMNESIA:33 report \cite{AMNESIA33}, which classifies it as one of the most resilient TCP/IP stack. By using as a starting point such a well-tested and widely used TCP/IP implementation, the IoT industry can have an immediate benefit by adopting this work's security-enhanced version of the CycloneTCP library.

@@

@@

%\subsection{TCP state machine}

Generally, every TCP communication session will go through the following three phases (if no error occurs): 1)~opening the connection 2)~sending and receiving
the data and 3)~closing the connection. The behavior of the three-phase communication can be described by the state machine in \cref{Fig:statemachine}.
